---
title: "Data Analysis"
output: html_notebook
---

Import necessary libraries.

```{r}

# install_keras() - don't want to install keras until we've determined
# we want to use it because keras is quite large.

library(readr)
library(data.table)
library(TermDataAnalysis)
library(keras)
library(parsnip)
library(tidyverse)
library(modeldata)


```

Then, we can import the data.

```{r}
onlineShopperData <- fread("data/online_shoppers_intention.csv")
data_processed <- copy(onlineShopperData)
```


Pre-process the data
```{r}

# First we trim the columns we don't need at all
data_processed <- stripUseless(onlineShopperData, c("OperatingSystems", 
                    "Browser", "Administrative", "Informational", 
                    "ProductRelated"))

# Then we combine the columsn that we think we can combine
# WARNING: The generalization for this function isn't set up yet TODO
data_processed <- proportionalize(onlineShopperData, c("ProductRelated_Duration",
                      "Administrative_Duration", "Informational_Duration", 
                      "ProductRelated_Duration"))

data_processed <- data_processed[, c(
                      "Administrative_Duration", "Informational_Duration", 
                      "ProductRelated_Duration") := NULL]

```


Build models identical to Sakar, but on our preprocessed version of the data
We need to try building 
1. MultiLayer Perceptron
2. SVM
3. Decision Trees

Initially, we'll split the data into 70% training set and 30% validation, just like
in Sakar.

```{r}

# source for examples https://www.r-bloggers.com/2024/09/how-to-split-a-data-frame-in-r-a-comprehensive-guide-for-beginners/
set.seed(123)

sample_size <- floor(0.7 * nrow(data_processed))
train_indices <- sample(seq_len(nrow(data_processed)), size = sample_size)

train_data <- data_processed[train_indices,]
test_data <- data_processed[-train_indices,]


```


1. Multilayer Perceptron
```{r}

# Make a simple mlp

mlp1 <- parsnip::mlp() %>%
  parsnip::set_engine("keras") %>%
  parsnip::set_mode("classification")

update(mlp1, hidden_units = 10)



```

Compare results

Use oversampling

Reconstruct models

Compare

If time use SMOTE?

Reconstruct models

Compare

Significantly reduce the size of the training set

Rebuild the models 

Compare


