---
title: "Data Analysis"
output: html_notebook
---

Import necessary libraries.

```{r}

# install_keras() - don't want to install keras until we've determined
# we want to use it because keras is quite large.

library(readr)
library(data.table)
library(TermDataAnalysis)
# library(keras)


```

Then, we can import the data.

```{r}
onlineShopperData <- fread("data/online_shoppers_intention.csv")
data_processed <- copy(onlineShopperData)
```


Pre-process the data
```{r}

# First we trim the columns we don't need at all
data_processed <- stripUseless(onlineShopperData, c("OperatingSystems", 
                    "Browser", "Administrative", "Informational", 
                    "ProductRelated"))

# Then we combine the columsn that we think we can combine
# WARNING: The generalization for this function isn't set up yet TODO
data_processed <- proportionalize(onlineShopperData, "ProductRelated_Duration", 
                    c("Administrative_Duration", "Informational_Duration", 
                      "ProductRelated_Duration"))

```


Build models identical to Sakar, but on our preprocessed version of the data
We need to try building 
1. MultiLayer Perceptron
2. SVM
3. Decision Trees
```{r}




```

Compare results

Use oversampling

Reconstruct models

Compare

If time use SMOTE?

Reconstruct models

Compare

Significantly reduce the size of the training set

Rebuild the models 

Compare


